---
title: "Get data for Tax Report"
output: html_notebook
---

This file is used to get the data for the Tax Report. It gets the data from:
a. The files from the batcht v9.
b. The API from the site.

## a) Get Data from batch v9.

```{r READ FILES}
IND = read.csv("GovData360IND_Enviov9.csv")
Data.a = read.csv("GovData360_Envio v9.csv")
library(dplyr)
```

```{r FILTER}
IND = IND %>% filter(Report == 'Yes')
Data.a = Data.a[(Data.a$Indicator_Code %in% IND$Indicator_Code), ]
unique(Data.a$Indicator_Code)
```
We need in the table the variables Value type and units. 

```{r Merge IND and values file}
Data.a = merge(Data.a, IND[, c(2,10,11,12)], by = 'Indicator_Code', all.x = T)
```


From the Data.a file it only match with those with overlap = GOV. I will have to query the rest from the API. Continue reading...

## b) Get Data from API

```{r}
library(data360r)
df_indicators <- get_metadata360(site="gov", metadata_type = "indicators")
List.of.ind.API = c('435', '28821', '24840', '437', '433', '433', '302', '24952', '281', '307', '306', '636', '635', '638', '637')

Data.b.wide <- get_data360(indicator_id= List.of.ind.API)
```

This data is in wide format. Let's transform it to long.

```{r}
library(reshape2)
Data.b.Long = melt(Data.b.wide, id.vars = c("Country ISO3", "Country Name", "Indicator", "Subindicator Type"))
Data.b = Data.b.Long
```

## Join both table

First, we will have to format them so they have the same format. We will use the format of the API as the standard.

```{r}
#Data.a
Data.a$X = NULL
Data.a$Indicator_Id.old. = NULL
Data.a$indicator = NULL
Data.a$subset = NULL
Data.a$group = NULL
Data.a$Indicator_Name = NULL
Data.a$Indicator_Id = NULL
Data.a$dataset = NULL
Data.a$Value_Type_Slug = NULL
Data.a$Units = NULL
#Rename columns
colnames(Data.a)[4] = 'Indicator'
colnames(Data.a)[2] = 'Country ISO3'
colnames(Data.a)[7] = 'Subindicator Type'

# Data.b
Data.b$answer = ''
Data.b$Indicator_Code = ''
colnames(Data.b)[5] = 'year'
Data.b$`Country Name` = NULL

Data.b$year[Data.b$year == '2007-2008'] = '2008'
Data.b$year[Data.b$year == '2008-2009'] = '2009'
Data.b$year[Data.b$year == '2009-2010'] = '2010'
Data.b$year[Data.b$year == '2010-2011'] = '2011'
Data.b$year[Data.b$year == '2011-2012'] = '2012'
Data.b$year[Data.b$year == '2012-2013'] = '2013'
Data.b$year[Data.b$year == '2013-2014'] = '2014'
Data.b$year[Data.b$year == '2014-2015'] = '2015'
Data.b$year[Data.b$year == '2015-2016'] = '2016'
Data.b$year[Data.b$year == '2016-2017'] = '2017'
Data.b$year[Data.b$year == '2017-2018'] = '2018'

setdiff(colnames(Data.a), colnames(Data.b))
setdiff(colnames(Data.b), colnames(Data.a))

Data.b = Data.b[ , c("Indicator_Code", "Country ISO3", "year", "Indicator", "answer", "value", "Subindicator Type")]

library(gtools)

Data.b$Indicator_Code = as.character(Data.b$Indicator_Code)
Data.b$`Country ISO3` = as.factor(Data.b$`Country ISO3`)
Data.b$year = as.character(Data.b$year)
Data.a$Indicator_Code = as.factor(Data.a$Indicator_Code)
Data.a$Indicator = as.character(Data.a$Indicator)

Data = smartbind(Data.a, Data.b)

#Drop values = NA
Data = Data[is.na(Data$value) != T,]
#Drop values = NA
Data = Data[Data$year != 'NA',]
```


```{r}
Data$Indicator = as.character(Data$Indicator)
Data$Indicator_Code[Data$Indicator == 'Paying Taxes: Payments number per year'] = 'DB42'
Data$Indicator_Code[Data$Indicator == 'Paying Taxes: Postfiling'] = 'DB43'
Data$Indicator_Code[Data$Indicator == 'Paying Taxes: Time hours per year'] = 'DB45'
Data$Indicator_Code[Data$Indicator == 'Paying Taxes: Total tax rate % of profit'] = 'DB46'
Data$Indicator_Code[Data$Indicator == 'Paying Taxes'] = 'DB48'
Data$Indicator_Code[Data$Indicator == 'Regulations and Taxes / If there were visits average number of visits or required meetings with tax officials'] = 'ES28'
Data$Indicator_Code[Data$Indicator == 'Regulations and Taxes / Number of visits or required meetings with tax officials'] = 'ES40' 
Data$Indicator_Code[Data$Indicator == 'Corruption / Percent of firms expected to give gifts in meetings with tax officials'] = 'ES45'
Data$Indicator_Code[Data$Indicator == 'Regulations and Taxes / Percent of firms identifying tax administration as a major constraint'] = 'ES66'
Data$Indicator_Code[Data$Indicator == 'Regulations and Taxes / Percent of firms identifying tax rates as a major constraint'] = 'ES67'
Data$Indicator_Code[(Data$Indicator == 'Effect of taxation on incentives to invest') & (Data$`Subindicator Type` == 'Rank')] = 'GCI94.1'
Data$Indicator_Code[(Data$Indicator == 'Effect of taxation on incentives to invest') & (Data$`Subindicator Type` == 'Value')] = 'GCI94.2'

Data$Indicator_Code[(Data$Indicator == 'Total tax rate % profits') & (Data$`Subindicator Type` == 'Rank')] = 'GCI95.1'
Data$Indicator_Code[(Data$Indicator == 'Total tax rate % profits') & (Data$`Subindicator Type` == 'Value')] = 'GCI95.2'

# In order to read without problems from Tableau...
Data$year = paste0("01/01/", Data$year)
```

## Validation

```{r}
str(Data)
a = Data[is.na(Data$Indicator_Code) == T, ]
a = Data[is.na(Data$`Country ISO3`) == T, ]
a = Data[is.na(Data$Indicator) == T, ]
a = Data[is.na(Data$answer) == T, ]
a = Data[is.na(Data$value) == T, ]
a = Data[is.na(Data$`Subindicator Type`) == T, ]
Dup = Data[(duplicated(Data[ , -7])) == T, ]
```

```{r}
write.csv(Data, "Data.csv")
```




